---
title: "Select Illumina human series for testing"
output: html_notebook
---

**J. Taroni 2018**

We'd like to try out some heuristics for automatically detecting platforms from
the probe identifiers. 
We'll need to sample the available series to see what's available in GEO.

Important limitations:

* Human only
* GEO only (i.e., no ArrayExpress)
* Only popular/official GPLs -- so we're not necessarily getting into weeds of
what's out there at this point
* Whole genome only at this point -- we'll need to add "Ref" platforms to fully
test out our ideas

```{r}
`%>%` <- dplyr::`%>%`
# directory that contains the list of series for each platform
series.dir <- file.path("data", "series_lists")
files <- list.files(series.dir, full.names = TRUE)
```

We'll grab 30 series from each of the 4 Illumina Human (whole genome) platforms.

```{r}
GetSampleSeriesDF <- function(filename, seed = 12345, n = 30) {
  set.seed(seed)
  df <- readr::read_tsv(filename)
  # only want things with supplemental files, drop methylation (IDAT) 
  # found some instances of CEL files, so restrict to TXT
  filt.df <- df %>%
    dplyr::filter(`Supplementary Types` == "TXT")
  sample.index <- sample(x = 1:nrow(filt.df), size = n)
  sampled.df <- filt.df[sample.index, ]
}
```

```{r}
set.seed(5)
seeds <- sample(1:10000, length(files))
```

```{r}
sample.df.list <- list()
for (seed.index in seq_along(seeds)) {
  fl <- files[seed.index]
  sample.df.list[[fl]] <- GetSampleSeriesDF(filename = fl, 
                                            seed = seeds[seed.index])
}
```

```{r}
lapply(sample.df.list, dim)
```

```{r}
dir.create("results") 
```

```{r}
for (list.index in seq_along(sample.df.list)) {
  new.fl <- file.path("results", 
                      sub("data/series_lists", "", 
                          sub("series.tsv", "series_sampled.tsv", 
                              names(sample.df.list)[list.index])))
  readr::write_tsv(sample.df.list[[list.index]], path = new.fl)
  # if there are any "non-normalized" files... we're gonna want to wget them
  urls <- paste(sample.df.list[[list.index]]$`Supplementary Links`,
                 "*non*", sep = "/")
  readr::write_lines(urls, path = sub("sampled.tsv", "urls", new.fl))
}
```

```{bash}
# Human-6 v1
mkdir -p data/series_non-normalized/GPL2507
FILE="results/GPL2507_series_urls"
while IFS=' ' read -r url
do
  wget --directory-prefix="data/series_non-normalized/GPL2507" $url
done < "$FILE"

# Human-6 v2
mkdir -p data/series_non-normalized/GPL6102
FILE="results/GPL6102_series_urls"
while IFS=' ' read -r url
do
  wget --directory-prefix="data/series_non-normalized/GPL6102" $url
done < "$FILE"

# HumanHT-12 v3
mkdir -p data/series_non-normalized/GPL6947
FILE="results/GPL6947_series_urls"
while IFS=' ' read -r url
do
  wget --directory-prefix="data/series_non-normalized/GPL6947" $url
done < "$FILE"

# HumanHT-12 v4
mkdir -p data/series_non-normalized/GPL10558
FILE="results/GPL10558_series_urls"
while IFS=' ' read -r url
do
  wget --directory-prefix="data/series_non-normalized/GPL10558" $url
done < "$FILE"
```

