---
title: "Plotting highlighting GEO Series that differ from expectations"
output: html_notebook
---

There were some GEO Series that had overlap calculations that differed from
what we would expect if they were entirely consistent with their platform
labels. 
We've manually inspected the results. 
Here we're going to change the fill on the jitter plot to highlight these 
accessions. 
This will make presenting the results easier.

### Read in data & mutate

Overlaps have already been calculated.

```{r}
`%>%` <- dplyr::`%>%`
overlap.df <- readr::read_tsv(file.path("results", "probe_id_overlap.tsv"))
```

Here are the accessions we'd like to highlight: `GSE17241`, `GSE14295`, 
`GSE35102`, `GSE45331`, `GSE25580` `GSE34074`, `GSE62374`, `GSE39417`, 
`GSE54661`

```{r}
highlight.df <- 
  overlap.df %>%
    dplyr::mutate(series = 
                    dplyr::case_when(
                      series_accession %in% c("GSE17241", "GSE17241.1") ~ "GSE17241 GPL2507",
                      series_accession == "GSE17241.2" ~ "GSE17241 GPL6106",
                      series_accession %in% c("GSE17241.3", "GSE17241.4") ~ "GSE17241 GPL6102",
                      series_accession %in% c("GSE14295", "GSE14295.1") ~ "GSE14295",
                      series_accession == "GSE35102" ~ "GSE35102",
                      series_accession == "GSE45331" ~ "GSE45331",
                      series_accession == "GSE25580" ~ "GSE25580 GPL6947",
                      series_accession == "GSE25580.1" ~ "GSE25580 GPL6104",
                      series_accession %in% c("GSE34074", "GSE34074.1") ~ "GSE34074 GPL6947",
                      series_accession %in% c("GSE34074.2", "GSE34074.3", "GSE34074.4") ~ "GSE34074 GPL10558",
                      series_accession == "GSE62374" ~ "GSE62374", 
                      series_accession == "GSE39417" ~ "GSE39417",
                      series_accession == "GSE54661" ~ "GSE54661",
                      TRUE ~ "other"
                    ))
```

### Plot

```{r}
set.seed(1234)  # for plot jitter
```

```{r}
dplyr::filter(highlight.df, geo_gpl == "GPL2507") %>%
  ggplot2::ggplot(ggplot2::aes(x = bioc_package,
                               y = value,
                               colour = series)) +
  ggplot2::geom_jitter(alpha = 0.5, width = 0.2) +
  ggplot2::facet_wrap(geo_gpl ~ metric, ncol = 2) +
  ggplot2::theme_bw() +
  ggplot2::scale_colour_manual(values = c(colorblindr::palette_OkabeIto[1:3],
                                          "#000000")) +
  ggplot2::labs(title = "Illumina Human Whole Genome BeadArray",
                x = "Bioconductor package", y = "% Overlap") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1,
                                                     vjust = 0.5))
```

```{r}
ggplot2::ggsave(file.path("plots", "GPL2507_jitter_highlight.png"),
                          width = 7, height = 5)
```


```{r}
dplyr::filter(highlight.df, geo_gpl == "GPL6102") %>%
  ggplot2::ggplot(ggplot2::aes(x = bioc_package,
                               y = value,
                               colour = series)) +
  ggplot2::geom_jitter(alpha = 0.5, width = 0.2) +
  ggplot2::facet_wrap(geo_gpl ~ metric, ncol = 2) +
  ggplot2::theme_bw() +
  ggplot2::scale_colour_manual(values = c(colorblindr::palette_OkabeIto[1:3],
                                          "#000000")) +
  ggplot2::labs(title = "Illumina Human Whole Genome BeadArray",
                x = "Bioconductor package", y = "% Overlap") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1,
                                                     vjust = 0.5))
```

```{r}
ggplot2::ggsave(file.path("plots", "GPL6102_jitter_highlight.png"),
                width = 7, height = 5)
```

```{r}
dplyr::filter(highlight.df, geo_gpl == "GPL6947") %>%
  ggplot2::ggplot(ggplot2::aes(x = bioc_package,
                               y = value,
                               colour = series)) +
  ggplot2::geom_jitter(alpha = 0.5, width = 0.2) +
  ggplot2::facet_wrap(geo_gpl ~ metric, ncol = 2) +
  ggplot2::theme_bw() +
  ggplot2::scale_colour_manual(values = c(colorblindr::palette_OkabeIto[1:4],
                                          "#000000")) +
  ggplot2::labs(title = "Illumina Human Whole Genome BeadArray",
                x = "Bioconductor package", y = "% Overlap") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1,
                                                     vjust = 0.5))
```

```{r}
ggplot2::ggsave(file.path("plots", "GPL6947_jitter_highlight.png"),
                width = 7, height = 5)
```

```{r}
dplyr::filter(highlight.df, geo_gpl == "GPL10558") %>%
  ggplot2::ggplot(ggplot2::aes(x = bioc_package,
                               y = value,
                               colour = series)) +
  ggplot2::geom_jitter(alpha = 0.5, width = 0.2) +
  ggplot2::facet_wrap(geo_gpl ~ metric, ncol = 2) +
  ggplot2::theme_bw() +
  ggplot2::scale_colour_manual(values = c(colorblindr::palette_OkabeIto[1:3],
                                          "#000000")) +
  ggplot2::labs(title = "Illumina Human Whole Genome BeadArray",
                x = "Bioconductor package", y = "% Overlap") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, hjust = 1,
                                                     vjust = 0.5))
```

```{r}
ggplot2::ggsave(file.path("plots", "GPL10558_jitter_highlight.png"),
                width = 7, height = 5)
```
